---
title: "Markov Language Chains"
author: "Kylei Hoffland, Camille Kich, Brandon Winder, Alex Mix"
date: "5/12/2020"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(rvest)
library(stringr)
library(tm)
library(lubridate)
library(tidytext)
set.seed(15)
```

```{r, include=FALSE}
source("sourcecode.R")
```

## Read In and Clean the Data

The wine reviews that we selected for our project were the daily picks for wine less than $15. We decided this was a good category as college students are often short on extra cash.

We started by scraping the reviews from https://www.winespectator.com/dailypicks/category/catid/1, we then separated out the review date, wine name, score, cost, review, when to drink, and how many cases were made/imported.
We ended up with a dataframe that looked like this:

```{r, echo=FALSE}
head(all_reviews)
```

## First Order Markov Chain

The review generation function for the first order Markov chain takes in a starting word, number of sentences, and probability for subsequent words. It works by randomly choosing the first word from the list of first words of real reviews, and generating the next word based on the transition probabilities. The probabilities are calculated from the chance that the current word in the state space will transition to another word in the state space. The state space is every word or punctuation mark used in the collection of real wine reviews.

Initially, the reviews generated were just a few sentences, but since the real reviews contain a date, score, price, when to drink, and number of cases produced, we also generated those additions to the reviews, making them look more like believable wine reviews written by real people.

To incorporate the type of wine, we compared the name of each wine associated with the review to a list of common types of wine reviewed on Wine Spectator. We then used this to sort out the wine by color and generated reviews just based on the state space of that specific colors, in this case white wines.by

```{r, echo=FALSE}
head(generated_reviews)
```

## Second Order Markov Chain

The review generation for the second order Markov chain works almost the same as the first, the only difference being that the next word (or punctuation) depends on the previous two. This initially generated massive reviews, likely because of a lower probability of "." in the state space. We set a limit to the number of words in each review to combat this.

We also added date, score, price, when to drink, and number of cases produced to the second order generated reviews to make them look more like reasonable reviews.

```{r, echo=FALSE}
head(generated_reviews2)
```

## Best, Worst, and Funniest Reviews

While most of our reviews turned out pretty well, some were better than others. Here are the reviews that we thought were the best, worst, and funniest.

# First-Order Markov chain reviews that were the best, and actually made sense:

[1] "2018-11-10, Score: 88, $14, Smooth shadow black licorice notes in this red shows hints of effervescence to the finish. Fun, with lime granita and sémillon. Drink now through 2020. 30,000 cases made."

[2] "2019-02-27, Score: 87, $12, Honeysuckle tobacco leaf notes are joined by crisp yet succulent peach flavors. Jalapeño mingling at the finish, with dried herb notes that balances melon, peppery notes echo. Drink now. 15,000 cases made."

[3] "2018-04-25, Score: 86, $14, Toasty perfumed white. Cocoa powder accents show on blast of earth notes of saline adding depth through the finish. Drink now through 2024. 60,000 cases made."

[4] "2019-11-12, Score: 85, $12, Wild array of elderflower. Bright on the finish. Drink now. 21,000 cases made, 21,000 cases imported."

[5] "2020-03-06, Score: 87, $13, Smoky toasty notes of olive accent juicy finish. Notes frame in the palate. Drink now. 8,000 cases imported."

[6] "2017-10-27, Score: 86, $13, Gentle fruity style, stony-laced oak, light tannins. Lemon and red, supported by ripe white raspberry and satisfying. Drink now through 2020. 53,900 cases made." 

# First-Order Markov chain reviews that were the worst, did not make any sense:

[1] "2017-05-19, Score: 85, $11, Pepper stream through the finish. The stage for the finish. Drink now. 10,000 cases imported."

[2] "2018-01-12, Score: 87, $12, Lithe exuberant juiciness enlivening the heady. Zesty cherry and blueberry and dried savory edge marks the finish. Drink now through 2019. 1,500 cases made."

[3] "2018-08-10, Score: 86, $10, Plum filled with petrol and mocha notes, grippy tannins show on the finish. Lively cava is full-lime and grilled meat, with lively cherry, with clean finish is mixed together by spice and creamy feel, key lime notes, showing vibrancy and citrusy, detailed by well-integrated acidity, with hints of meyer lemon peel acidity and straightforward and berry and ruby grapefruit aromas and savory spice elements in this light-to the finish. Drink now through 2022. 20,000 cases made."

[4] "2019-04-04, Score: 87, $14, Vividly shortbread-dried herb, medium-to medium-bodied red. Succulent, easygoing and balanced crowd-driven note of kiwifruit, grated ginger notes emerge on smoky and grassy details are smooth, but are tied to medium-drinking flavors with black cherry flavors. Drink now. 5,000 cases made."

[5] "2018-08-09, Score: 88, $12, Cumin ride the creamy mousse details, marmalade and refreshing on the lightly aromatic thread in this lightly zesty and juicy and clamp down on lime and tar and concentrated, catarratto and meyer lemon flavors of candied lemon-toned and quince flavors. Merlot. Drink now through 2023. 5,500 cases made."

# First-Order Markov chain reviews that were funny or extra weird sounding:

[1] "2018-05-24, Score: 87, $13, Racy tasty but fresh. Taut tannins mark the finish. Drink now. 4,000 cases imported."

[2] "2019-07-27, Score: 87, $13, Marshmallow quick finish. Lively, fig flavors. Drink now. 20,000 cases made."

[3] "2018-01-19, Score: 88, $12, Lushly detail the raspberry flavors in on the finish. Leathery hints of forest floor flavors are softly juicy acidity give this round and herbal notes are flanked by hints. Drink now. 391,000 cases made."

[4] "2017-04-24, Score: 86, $13, Floral sense of petrol and grapefruit notes on the flavors, anise and crowd-bodied red shows good length. Details. Drink now through 2019. 28,500 cases imported."

[5] "2017-08-09, Score: 87, $10, Racy peel flavors, with light tannins. Touch soft finish. Drink now. 3,500 cases made."

# Same for Second-Order Chain Reviews

# Second-Order Markov chain reviews that were the best, and actually made sense:

# Second-Order Markov chain reviews that were the worst, did not make any sense:

# Second-Order Markov chain reviews that were funny or extra weird sounding:


